Appendix

### 2025-03-14 manuscript_rmarkdown/manuscript_appendix.Rmd
Further progress on empirical central normality test.
Almost there :)

---
title: "Appendix"
author: "Alex Zwanenburg, Steffen Löck"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    keep_tex: true
papersize: a4
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{amsthm}
- \usepackage{booktabs}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

@@

\begin{definition}[empirical central normality test]

Let $\mathbf{X} = \left\{x_1, x_2, \ldots, x_n\right\} \in \mathbb{R}^n$ be a vector of length $n$,
sorted so that $x_1 \leq x_2 \leq \ldots \leq x_n$.
Let $p_i = \frac{i - 1/3}{n + 1/3}$, with $i = 1, 2, \ldots n$ be the percentile value
corresponding to each value in $\mathbf{X}$. For tied values in $\mathbf{X}$,
percentile values are replaced by the average in their group.
Let $z_i = F^{-1}_{\mathcal{N}}(p_i)$ be the corresponding z-score, derived from the quantile function of the normal distribution.

@@

Critical values for the test statistics of the empirical central normality test 
are found in Table \ref{tab:empirical-central-normality-critical-statistic}.

@@

\midrule
    5 & 24.02 & 21.26 & 17.37 & 14.02 & 12.04 &  9.57 &  7.64 &  5.54 & 2.35 \\
   10 & 21.58 & 18.53 & 13.82 & 10.23 &  8.75 &  7.65 &  6.79 &  5.87 & 4.23 \\
   20 & 15.12 & 13.17 & 10.03 &  7.74 &  6.80 &  6.13 &  5.58 &  5.04 & 4.07 \\
   50 &  9.99 &  8.70 &  6.69 &  5.26 &  4.67 &  4.26 &  3.92 &  3.59 & 3.02 \\
  100 &  7.13 &  6.21 &  4.83 &  3.79 &  3.38 &  3.08 &  2.87 &  2.63 & 2.24 \\ 
  200 &  5.19 &  4.54 &  3.51 &  2.77 &  2.47 &  2.26 &  2.09 &  1.92 & 1.65 \\ 
  500 &  3.47 &  3.06 &  2.38 &  1.86 &  1.65 &  1.51 &  1.40 &  1.28 & 1.08 \\
 1000 &  2.65 &  2.35 &  1.84 &  1.44 &  1.27 &  1.16 &  1.07 &  0.98 & 0.81 \\
 2000 &  2.13 &  1.91 &  1.53 &  1.20 &  1.06 &  0.96 &  0.88 &  0.79 & 0.65 \\
 5000 &  1.69 &  1.56 &  1.30 &  1.07 &  0.95 &  0.87 &  0.80 &  0.72 & 0.58 \\
10000 &  1.50 &  1.41 &  1.23 &  1.05 &  0.96 &  0.89 &  0.83 &  0.77 & 0.64 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

>>>>

---
title: "Appendix"
author: "Alex Zwanenburg, Steffen Löck"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    keep_tex: true
papersize: a4
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{amsthm}
- \usepackage{booktabs}
- \newtheorem{definition}{Definition}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

@@

\begin{definition}[central portion of a sequence]
Let $\mathbf{X} = \left\{x_1, x_2, \ldots, x_n | x_i \in \mathbb{R}\right\}$ be a finite sequence of length $n > 0$,
ordered so that $x_1 \leq x_2 \leq \ldots \leq x_n$.
Let $p_i = \frac{i - 1/3}{n + 1/3}$, with $i = 1, 2, \ldots n$ be the percentile value
corresponding to each element in $\mathbf{X}$. For elements with tied values in $\mathbf{X}$,
percentile values are replaced by the average in their group, i.e.
if $x_j = x_{j+1} = \ldots = x_{j+m}$, then 
$p_j' = p_{j+1}' = \ldots = p_{j+m}' = 1/(m+1)\sum_j^{j+m}p_j$.
Furthermore, let central portion $\kappa \in (0,1)$.

Then the central portion of $\mathbf{X}$ is 
$\mathbf{X}_{\text{c}} = \left\{x_i \in \mathbf{X} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

@@

\begin{definition}[Residual errors of the central portion of a sequence]

Let the residual error for each element of $\mathbf{X}$ be $r_i =\left| \frac{x_i - \mu_M}{\sigma_M} - F^{-1}_{\mathcal{N}}(p_i) \right|$, 
with $\mu_M$ and $\sigma_M$ robust Huber M-estimates of location and scale of $\mathbf{X}$ [@Huber1981-su], 
and $F^{-1}_{\mathcal{N}}$ the quantile function of the normal distribution $\mathcal{N}(0, 1)$.

Then, the set of residual errors of the central portion of $\mathbf{X}$ (i.e. $\mathbf{X}_{\text{c}}$) is
$\mathbf{R}_{\text{c}} = \left\{ r_i \in \left\{ r_1, r_2, \ldots, r_n\right\} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

\begin{definition}[Central normality of a sequence]

The central portion of a sequence is normally distributed if the sum of residual
errors is equal to zero:
$\sum_{r_j \in \mathbf{R}_{\text{c}}} r_j = 0$

In practice, a finite sequence sampled from a normal distribution $\mathcal{N}(\mu, \sigma)$ will have a non-zero sum of residual errors.

\begin{definition}[Empirical central normality test]
$\mathcal{H}_0: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j = 0$

$\mathcal{H}_1: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j > 0$
\end{definition}

The null-hypothesis $\mathcal{H}_0$ is that the central portion of sequence $\mathbf{X}$
is normally distributed, with the alternative hypothesis $\mathcal{H}_1$ that it
is not normally distributed. To test this hypothesis, a test statistic is computed
and compared against a critical value.

\begin{definition}[Empirical central normality test statistic]
Let $\alpha$ be the significance level for the empirical central normality test.
Let $m$ be the number of elements of $\mathbf{R}_{\text{c}}$

The test statistic is then $\tau_{\text{ecn}, \alpha, n, \kappa} = \frac{1}{m}\sum_{r_j \in \mathbf{R}_{\text{c}}}r_j$.

Critical values for the test statistic of the empirical central normality test 
are found in Table \ref{tab:empirical-central-normality-critical-statistic}. 
The null-hypothesis should be rejected at significance level $\alpha$ if 
$\tau_{\text{ecn}, \alpha, n, \kappa} \geq \tau_{\text{ecn}, \alpha, n, \kappa, \text{critical}}$.

```{r include = FALSE, eval = FALSE}
# This writes the lookup table for critical test statistic.
load(file = "./R/sysdata.rda")

gof_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = FALSE
)

usethis::use_data(
  gof_lookup_table, 
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = TRUE
)

@@

\midrule
5     & 25.28 & 22.17 & 17.46 & 13.15 & 10.48 & 8.32 & 6.62 & 4.93 & 2.24 \\
10    & 21.11 & 18.16 & 13.66 & 10.14 &  8.67 & 7.59 & 6.74 & 5.89 & 4.12 \\
20    & 14.93 & 12.96 &  9.97 &  7.71 &  6.77 & 6.11 & 5.56 & 5.02 & 3.97 \\
50    &  9.69 &  8.49 &  6.59 &  5.20 &  4.63 & 4.22 & 3.91 & 3.58 & 2.99 \\
100   &  6.92 &  6.06 &  4.71 &  3.73 &  3.32 & 3.04 & 2.83 & 2.59 & 2.20 \\
200   &  4.89 &  4.29 &  3.35 &  2.66 &  2.37 & 2.17 & 2.02 & 1.87 & 1.60 \\
500   &  3.12 &  2.73 &  2.12 &  1.69 &  1.51 & 1.39 & 1.29 & 1.19 & 1.02 \\
1000  &  2.19 &  1.92 &  1.50 &  1.20 &  1.07 & 0.98 & 0.92 & 0.85 & 0.73 \\
2000  &  1.56 &  1.37 &  1.06 &  0.85 &  0.76 & 0.70 & 0.65 & 0.60 & 0.52 \\
5000  &  0.99 &  0.86 &  0.67 &  0.54 &  0.48 & 0.44 & 0.41 & 0.38 & 0.32 \\
10000 &  0.69 &  0.61 &  0.48 &  0.38 &  0.34 & 0.31 & 0.29 & 0.27 & 0.23 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

### 2025-03-14 manuscript_rmarkdown/manuscript_appendix.tex
Further progress on empirical central normality test.
Almost there :)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{booktabs}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\sgn}{sgn}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Appendix},
  pdfauthor={Alex Zwanenburg, Steffen Löck},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Appendix}
\author{Alex Zwanenburg, Steffen Löck}
\date{2025-03-13}

@@

@@

\toprule
$n$ \ $\alpha$ & 0.1 & 0.2 & 0.5 & 0.8 & 0.9 & 0.95 & 0.975 & 0.99 & 0.999 \\

\midrule
    5 & 24.02 & 21.26 & 17.37 & 14.02 & 12.04 &  9.57 &  7.64 &  5.54 & 2.35 \\
   10 & 21.58 & 18.53 & 13.82 & 10.23 &  8.75 &  7.65 &  6.79 &  5.87 & 4.23 \\
   20 & 15.12 & 13.17 & 10.03 &  7.74 &  6.80 &  6.13 &  5.58 &  5.04 & 4.07 \\
   50 &  9.99 &  8.70 &  6.69 &  5.26 &  4.67 &  4.26 &  3.92 &  3.59 & 3.02 \\
  100 &  7.13 &  6.21 &  4.83 &  3.79 &  3.38 &  3.08 &  2.87 &  2.63 & 2.24 \\ 
  200 &  5.19 &  4.54 &  3.51 &  2.77 &  2.47 &  2.26 &  2.09 &  1.92 & 1.65 \\ 
  500 &  3.47 &  3.06 &  2.38 &  1.86 &  1.65 &  1.51 &  1.40 &  1.28 & 1.08 \\
 1000 &  2.65 &  2.35 &  1.84 &  1.44 &  1.27 &  1.16 &  1.07 &  0.98 & 0.81 \\
 2000 &  2.13 &  1.91 &  1.53 &  1.20 &  1.06 &  0.96 &  0.88 &  0.79 & 0.65 \\
 5000 &  1.69 &  1.56 &  1.30 &  1.07 &  0.95 &  0.87 &  0.80 &  0.72 & 0.58 \\
10000 &  1.50 &  1.41 &  1.23 &  1.05 &  0.96 &  0.89 &  0.83 &  0.77 & 0.64 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\newtheorem{definition}{Definition}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\sgn}{sgn}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Appendix},
  pdfauthor={Alex Zwanenburg, Steffen Löck},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Appendix}
\author{Alex Zwanenburg, Steffen Löck}
\date{2025-03-14}

@@

\begin{definition}[central portion of a sequence]
Let $\mathbf{X} = \left\{x_1, x_2, \ldots, x_n | x_i \in \mathbb{R}\right\}$ be a finite sequence of length $n > 0$,
ordered so that $x_1 \leq x_2 \leq \ldots \leq x_n$.
Let $p_i = \frac{i - 1/3}{n + 1/3}$, with $i = 1, 2, \ldots n$ be the percentile value
corresponding to each element in $\mathbf{X}$. For elements with tied values in $\mathbf{X}$,
percentile values are replaced by the average in their group, i.e.
if $x_j = x_{j+1} = \ldots = x_{j+m}$, then 
$p_j' = p_{j+1}' = \ldots = p_{j+m}' = 1/(m+1)\sum_j^{j+m}p_j$.
Furthermore, let central portion $\kappa \in (0,1)$.

Then the central portion of $\mathbf{X}$ is 
$\mathbf{X}_{\text{c}} = \left\{x_i \in \mathbf{X} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

\end{definition}

\begin{definition}[Residual errors of the central portion of a sequence]

Let the residual error for each element of $\mathbf{X}$ be $r_i =\left| \frac{x_i - \mu_M}{\sigma_M} - F^{-1}_{\mathcal{N}}(p_i) \right|$, 
with $\mu_M$ and $\sigma_M$ robust Huber M-estimates of location and scale of $\mathbf{X}$ [@Huber1981-su], 
and $F^{-1}_{\mathcal{N}}$ the quantile function of the normal distribution $\mathcal{N}(0, 1)$.

Then, the set of residual errors of the central portion of $\mathbf{X}$ (i.e. $\mathbf{X}_{\text{c}}$) is
$\mathbf{R}_{\text{c}} = \left\{ r_i \in \left\{ r_1, r_2, \ldots, r_n\right\} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

\end{definition}

\begin{definition}[Central normality of a sequence]

The central portion of a sequence is normally distributed if the sum of residual
errors is equal to zero:
$\sum_{r_j \in \mathbf{R}_{\text{c}}} r_j = 0$

\end{definition}

In practice, a finite sequence sampled from a normal distribution
\(\mathcal{N}(\mu, \sigma)\) will have a non-zero sum of residual
errors.

\begin{definition}[Empirical central normality test]
$\mathcal{H}_0: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j = 0$

$\mathcal{H}_1: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j > 0$
\end{definition}

The null-hypothesis \(\mathcal{H}_0\) is that the central portion of
sequence \(\mathbf{X}\) is normally distributed, with the alternative
hypothesis \(\mathcal{H}_1\) that it is not normally distributed. To
test this hypothesis, a test statistic is computed and compared against
a critical value.

\begin{definition}[Empirical central normality test statistic]
Let $\alpha$ be the significance level for the empirical central normality test.
Let $m$ be the number of elements of $\mathbf{R}_{\text{c}}$

The test statistic is then $\tau_{\text{ecn}, \alpha, n, \kappa} = \frac{1}{m}\sum_{r_j \in \mathbf{R}_{\text{c}}}r_j$.

\end{definition}

Critical values for the test statistic of the empirical central
normality test are found in Table
\ref{tab:empirical-central-normality-critical-statistic}. The
null-hypothesis should be rejected at significance level \(\alpha\) if
\(\tau_{\text{ecn}, \alpha, n, \kappa} \geq \tau_{\text{ecn}, \alpha, n, \kappa, \text{critical}}\).

@@

\toprule
$n$ \textbackslash \~ $\alpha$ & 0.1 & 0.2 & 0.5 & 0.8 & 0.9 & 0.95 & 0.975 & 0.99 & 0.999 \\

\midrule
5     & 25.28 & 22.17 & 17.46 & 13.15 & 10.48 & 8.32 & 6.62 & 4.93 & 2.24 \\
10    & 21.11 & 18.16 & 13.66 & 10.14 &  8.67 & 7.59 & 6.74 & 5.89 & 4.12 \\
20    & 14.93 & 12.96 &  9.97 &  7.71 &  6.77 & 6.11 & 5.56 & 5.02 & 3.97 \\
50    &  9.69 &  8.49 &  6.59 &  5.20 &  4.63 & 4.22 & 3.91 & 3.58 & 2.99 \\
100   &  6.92 &  6.06 &  4.71 &  3.73 &  3.32 & 3.04 & 2.83 & 2.59 & 2.20 \\
200   &  4.89 &  4.29 &  3.35 &  2.66 &  2.37 & 2.17 & 2.02 & 1.87 & 1.60 \\
500   &  3.12 &  2.73 &  2.12 &  1.69 &  1.51 & 1.39 & 1.29 & 1.19 & 1.02 \\
1000  &  2.19 &  1.92 &  1.50 &  1.20 &  1.07 & 0.98 & 0.92 & 0.85 & 0.73 \\
2000  &  1.56 &  1.37 &  1.06 &  0.85 &  0.76 & 0.70 & 0.65 & 0.60 & 0.52 \\
5000  &  0.99 &  0.86 &  0.67 &  0.54 &  0.48 & 0.44 & 0.41 & 0.38 & 0.32 \\
10000 &  0.69 &  0.61 &  0.48 &  0.38 &  0.34 & 0.31 & 0.29 & 0.27 & 0.23 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
